\documentclass[10pt]{article}

\usepackage[margin=0.8in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{hyperref}
\usepackage{microtype}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  urlcolor=black
}

\title{\bfseries Supplementary Information\\Permitless Concealed Carry Adoption and Firearm Mortality in U.S. States, 1999--2024}
\author{Yucheng Wang and Byung Kim\\\textit{Both authors contributed equally to this work.}}
\date{June 2026}

\begin{document}
\maketitle

\section*{Supplementary Note 1. Evidence hierarchy}

The main manuscript interprets results through a hierarchy rather than treating every diagnostic row as an independent hypothesis test. Firearm suicide is the primary outcome. Total suicide, non-firearm suicide, firearm homicide, and total firearm deaths are secondary outcome-family checks. Firearm-law covariates, contextual covariate layers, age-adjusted outcome rates, staggered-adoption diagnostics, Arkansas recoding, leave-one-out influence, and placebo timing are sensitivity checks. Rurality, gun ownership, baseline-risk heterogeneity, and policy-feature interactions are exploratory. Cohort ATT rows, event-time rows, full legal source tables, and full robustness grids are appendix diagnostics.

\begin{center}
\begin{tabular}{p{0.20\linewidth}p{0.31\linewidth}p{0.34\linewidth}}
\toprule
Tier & Items & Interpretation \\
\midrule
Primary outcome & Firearm suicide & Central mortality claim. \\
Secondary outcomes & Total suicide; non-firearm suicide; firearm homicide; total firearm deaths & Specificity and outcome-family interpretation. \\
Sensitivity checks & Firearm-law covariates; health-access and overdose covariates; Phase 3B2 covariate layers; age-adjusted outcome rates; staggered-adoption diagnostics; Arkansas recoding; leave-one-out; placebo timing & Tests stability and boundaries. \\
Exploratory checks & Rurality, gun-ownership, baseline-risk, and policy-feature heterogeneity & Hypothesis-generating only. \\
Appendix diagnostics & Cohort ATT rows; event-time rows; legal source table; full robustness grids & Transparency and audit trail. \\
\bottomrule
\end{tabular}
\end{center}

\section*{Supplementary Note 2. Legal audit and policy-feature coding}

The legal audit records one row per state and distinguishes clean source-verified within-panel adopters from verified non-adopters, partial cases, ambiguous cases, and baseline-permitless states. Partial, ambiguous, and baseline-permitless rows are documented so that they are not silently absorbed into the binary treatment definition.

\begin{center}
\begin{tabular}{lr}
\toprule
Audit status & State count \\
\midrule
Source-verified current adopter & 26 \\
Verified non-adopter & 21 \\
Ambiguous reviewed & 1 \\
Partial & 1 \\
Baseline permitless & 1 \\
\bottomrule
\end{tabular}
\end{center}

Among the 26 clean source-verified adopter rows, 21 had a training requirement removed, 25 removed the carry-permit background-check screen, and 12 removed a permit-specific misdemeanor-violence screen. These policy-feature fields describe the carry-permit process and are treated as exploratory.

\begin{center}
\begin{tabular}{p{0.55\linewidth}r}
\toprule
Mechanism field/value & State count \\
\midrule
Training requirement removed: yes & 21 \\
Training requirement removed: no prior training requirement & 5 \\
Carry-permit background-check screen removed & 25 \\
Carry-permit screen removed while purchase permit retained & 1 \\
Permit-specific misdemeanor screen removed & 12 \\
Eligibility standard retained but no pre-carry check & 7 \\
Other misdemeanor-screen coding categories & 7 \\
\bottomrule
\end{tabular}
\end{center}

The full state-level audit below reports the adoption year, audit status, whether the state enters the primary processed treatment map, the coding note, and source URLs used for legal verification. This table is included to make Arkansas, Mississippi, and Vermont visible rather than hiding the edge cases inside a binary treatment variable.

\input{tables/treatment_coding_appendix.tex}

\section*{Supplementary Note 3. Main and secondary mortality estimates}

\begin{center}
\begin{tabular}{lrrrr}
\toprule
Outcome & Coef. & SE & $p$ & N \\
\midrule
Firearm suicide & 1.391 & 0.222 & $<0.001$ & 1222 \\
Non-firearm suicide & 0.415 & 0.139 & 0.003 & 1222 \\
Total suicide & 1.805 & 0.294 & $<0.001$ & 1222 \\
Firearm homicide & -0.234 & 0.338 & 0.489 & 1142 \\
Total firearm deaths & 1.271 & 0.482 & 0.008 & 1222 \\
\bottomrule
\end{tabular}
\end{center}

\section*{Supplementary Note 4. Firearm-suicide diagnostic spine}

The diagnostic spine places the baseline fixed-effects estimate beside population weighting, COVID-window restrictions, leave-one-adopter-out checks, placebo timing, state-specific trends, and staggered-adoption diagnostics. It is the main table for interpreting identification strength and fragility.

\input{tables/firearm_suicide_diagnostic_spine.tex}

\section*{Supplementary Note 5. Age-adjusted outcome-rate sensitivity}

Crude mortality rates are the primary outcome scale because they measure realized state-year mortality burden. Age-adjusted rates are reported as a demographic-composition sensitivity check using CDC WONDER age-adjusted rates standardized to the 2000 U.S. standard population. The age-adjusted estimates preserve the crude-rate pattern: firearm suicide, total suicide, and total firearm deaths remain positive, while firearm homicide remains statistically weak and centered below zero.

\begin{center}
\begin{tabular}{lrrrr}
\toprule
Outcome & Coef. & SE & $p$ & N \\
\midrule
Firearm suicide, age-adjusted & 1.407 & 0.228 & $<0.001$ & 1220 \\
Total suicide, age-adjusted & 1.914 & 0.327 & $<0.001$ & 1222 \\
Total firearm deaths, age-adjusted & 1.230 & 0.510 & 0.016 & 1222 \\
Firearm homicide, age-adjusted & -0.230 & 0.426 & 0.590 & 1037 \\
\bottomrule
\end{tabular}
\end{center}

\section*{Supplementary Note 6. Firearm-law and contextual covariate sensitivity}

External firearm-law covariates attenuated but did not erase the firearm-suicide estimate. Demographic-poverty covariates also preserved the firearm-suicide and total-suicide estimates. The short HRSA mental-health-provider window did not retain statistical significance and should be interpreted as a short-window sensitivity rather than a full-panel replacement. These rows are covariate-layer sensitivity checks, not uniformly superior causal models, because some time-varying covariates may lie downstream of broader state policy environments.

\begin{center}
\begin{tabular}{lrrr}
\toprule
Firearm-suicide specification & Coef. & $p$ & N \\
\midrule
Baseline fixed effects & 1.391 & $<0.001$ & 1222 \\
External firearm-law covariates & 1.096 & $<0.001$ & 1222 \\
Health-access covariates & 0.707 & $<0.001$ & 752 \\
Overdose covariates & 0.492 & 0.060 & 282 \\
Demographic-poverty covariates & 0.695 & $<0.001$ & 940 \\
Mental-health-provider access covariates & 0.116 & 0.744 & 141 \\
Full Phase 3B2 covariates & 0.176 & 0.633 & 141 \\
\bottomrule
\end{tabular}
\end{center}

\section*{Supplementary Note 7. Change-score checks}

\begin{center}
\begin{tabular}{lrrr}
\toprule
Outcome & 2-year diff. & 3-year diff. & 5-year diff. \\
\midrule
Firearm suicide & 0.658 & 0.634 & 0.699 \\
Non-firearm suicide & 0.214 & 0.134 & 0.047 \\
Total suicide & 0.872 & 0.767 & 0.746 \\
Firearm homicide & -0.034 & 0.024 & 0.035 \\
Total firearm deaths & 0.537 & 0.617 & 0.718 \\
\bottomrule
\end{tabular}
\end{center}

\section*{Supplementary Note 8. Staggered-adoption diagnostics}

\begin{center}
\begin{tabular}{lrrrrp{0.23\linewidth}}
\toprule
Outcome & ATT w2 & ATT w3 & ATT w5 & Not-yet post & Interpretation \\
\midrule
Firearm suicide & 0.601 & 0.577 & 0.641 & 0.387 & Positive post-adoption diagnostic with pretrend flag. \\
Non-firearm suicide & 0.270 & 0.239 & 0.241 & 0.077 & Positive post-adoption diagnostic. \\
Total suicide & 0.871 & 0.816 & 0.882 & 0.464 & Positive post-adoption diagnostic with pretrend flag. \\
Firearm homicide & -0.004 & -0.107 & -0.106 & -0.157 & No positive post-adoption diagnostic. \\
Total firearm deaths & 0.382 & 0.435 & 0.493 & 0.200 & Positive post-adoption diagnostic with pretrend flag. \\
\bottomrule
\end{tabular}
\end{center}

\section*{Supplementary Note 9. Robustness and Arkansas sensitivity}

\begin{center}
\begin{tabular}{lrrrrp{0.22\linewidth}}
\toprule
Outcome & Baseline & P05 specs & Leave-one min & Leave-one max & Flag \\
\midrule
Firearm suicide & 1.391 & 5 & 1.265 & 1.481 & Stable positive, trend-sensitive. \\
Non-firearm suicide & 0.415 & 5 & 0.371 & 0.472 & Stable positive, trend-sensitive. \\
Total suicide & 1.805 & 6 & 1.656 & 1.954 & Stable positive. \\
Firearm homicide & -0.234 & 0 & -0.399 & -0.049 & No stable positive signal. \\
Total firearm deaths & 1.271 & 4 & 1.058 & 1.532 & Positive, trend-sensitive. \\
\bottomrule
\end{tabular}
\end{center}

Arkansas recoding as 2021 or 2023 retained the sign of all five outcomes. Firearm suicide, total suicide, non-firearm suicide, and total firearm deaths retained $p<0.05$ across both Arkansas codings; firearm homicide did not. Reintroducing Mississippi alone and in combination with both Arkansas codings preserved the positive firearm-suicide and total-suicide pattern.

\begin{table}[H]
\centering
\caption{\textbf{Firearm-suicide leave-one-adopter-out estimates by excluded state.}}
\small
\begin{tabular}{lrr}
\toprule
Excluded state & Coef. & $p$ \\
\midrule
Alabama & 1.415 & $<0.001$ \\
Alaska & 1.405 & $<0.001$ \\
Arizona & 1.481 & $<0.001$ \\
Florida & 1.398 & $<0.001$ \\
Georgia & 1.413 & $<0.001$ \\
Idaho & 1.375 & $<0.001$ \\
Indiana & 1.393 & $<0.001$ \\
Iowa & 1.395 & $<0.001$ \\
Kansas & 1.414 & $<0.001$ \\
Kentucky & 1.451 & $<0.001$ \\
Louisiana & 1.411 & $<0.001$ \\
Maine & 1.399 & $<0.001$ \\
Missouri & 1.366 & $<0.001$ \\
Montana & 1.342 & $<0.001$ \\
Nebraska & 1.404 & $<0.001$ \\
New Hampshire & 1.391 & $<0.001$ \\
North Dakota & 1.358 & $<0.001$ \\
Ohio & 1.410 & $<0.001$ \\
Oklahoma & 1.383 & $<0.001$ \\
South Carolina & 1.406 & $<0.001$ \\
South Dakota & 1.403 & $<0.001$ \\
Tennessee & 1.416 & $<0.001$ \\
Texas & 1.415 & $<0.001$ \\
Utah & 1.424 & $<0.001$ \\
West Virginia & 1.420 & $<0.001$ \\
Wyoming & 1.265 & $<0.001$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{\textbf{Firearm-suicide never-treated placebo timing estimates.}}
\small
\begin{tabular}{rrr}
\toprule
Placebo shift & Coef. & $p$ \\
\midrule
0 & -0.026 & 0.850 \\
1 & -0.246 & 0.173 \\
2 & -0.062 & 0.788 \\
3 & 0.081 & 0.721 \\
4 & 0.385 & 0.060 \\
5 & 0.291 & 0.047 \\
6 & 0.054 & 0.675 \\
7 & 0.050 & 0.767 \\
8 & -0.032 & 0.883 \\
9 & -0.224 & 0.375 \\
10 & -0.275 & 0.156 \\
\bottomrule
\end{tabular}
\end{table}

The absolute median placebo estimate was 0.081 deaths per 100,000 and the absolute 95th percentile was 0.338. The observed firearm-suicide estimate was 1.391, exceeding that placebo timing distribution.

\section*{Supplementary Note 10. Heterogeneity and policy-feature checks}

Rurality was the clearest recurring heterogeneity dimension: firearm suicide, non-firearm suicide, and total suicide had positive high-rurality interactions. These models are exploratory because state-level subgroup indicators are coarse and adoption is politically patterned.

\begin{center}
\begin{tabular}{lrr}
\toprule
Outcome/dimension & Interaction & $p$ \\
\midrule
Firearm suicide, high rurality & 0.988 & $<0.001$ \\
Total suicide, high rurality & 1.733 & $<0.001$ \\
Non-firearm suicide, high rurality & 0.745 & $<0.001$ \\
Non-firearm suicide, high gun ownership & 0.586 & $<0.001$ \\
\bottomrule
\end{tabular}
\end{center}

Policy-feature heterogeneity did not identify a stable mechanism. None of the 15 training, carry-permit background-check, or misdemeanor-screen interaction rows had $p<0.05$. Five rows were sparse or unavailable because the feature-specific clean-adopter comparison group was absent.

\section*{Supplementary Note 11. Homicide missingness audit}

Firearm-homicide outcome rows have fewer observations than suicide and total-firearm rows because some state-year rates are unavailable or suppressed. The missingness audit shows that all missing firearm-homicide rows occur in the smallest-population state-years.

\input{tables/homicide_missingness_audit.tex}

\input{tables/homicide_missingness_by_state.tex}

\section*{Supplementary Note 12. Full diagnostic source files}

The following repository outputs provide the full machine-readable diagnostic trail used to write the manuscript and this supplement:

\begin{itemize}
\item \texttt{outputs/tables/did/twfe\_did\_main\_results.csv}
\item \texttt{outputs/tables/did/twfe\_did\_ageadj\_sensitivity\_summary.csv}
\item \texttt{outputs/tables/did/twfe\_did\_firearm\_law\_control\_summary.csv}
\item \texttt{outputs/tables/did/twfe\_did\_nonfirearm\_confounder\_summary.csv}
\item \texttt{outputs/tables/did/twfe\_did\_phase3b2\_confounder\_summary.csv}
\item \texttt{outputs/tables/main/welch\_change\_score\_results.csv}
\item \texttt{outputs/tables/modern\_did/modern\_did\_summary.csv}
\item \texttt{outputs/tables/modern\_did/event\_time\_never\_control\_estimates.csv}
\item \texttt{outputs/tables/robustness/robustness\_summary.csv}
\item \texttt{outputs/tables/robustness/leave\_one\_state\_out.csv}
\item \texttt{outputs/tables/robustness/placebo\_never\_treated.csv}
\item \texttt{outputs/tables/robustness/arkansas\_treatment\_sensitivity\_summary.csv}
\item \texttt{outputs/tables/heterogeneity/heterogeneity\_did\_results.csv}
\item \texttt{outputs/tables/mechanism/mechanism\_heterogeneity\_results.csv}
\item \texttt{data/policy/permitless\_carry\_legal\_audit.csv}
\end{itemize}

\end{document}
