\begingroup
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{longtable}{p{0.12\linewidth}p{0.08\linewidth}p{0.14\linewidth}p{0.08\linewidth}p{0.25\linewidth}p{0.25\linewidth}}
\caption{State-by-state permitless concealed-carry treatment coding audit.}\label{tab:full_treatment_coding}\\
\toprule
State & Year & Audit status & Primary map & Coding note & Source URL(s) \\
\midrule
\endfirsthead
\toprule
State & Year & Audit status & Primary map & Coding note & Source URL(s) \\
\midrule
\endhead
Alabama & 2023 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://legiscan.com/AL/text/HB272/id/2544995;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Alaska & 2003 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://dps.alaska.gov/Statewide/R-I/PermitsLicensing/Firearm-FAQ;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Arizona & 2010 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.azleg.gov/legtext/49leg/2r/bills/sb1108s.pdf;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Arkansas & -- & ambiguous reviewed & No & Excluded from primary clean-adoption map; 2021 and 2023 codings tested as sensitivities. & \detokenize{https://arkleg.state.ar.us/Bills/Detail?ddBienniumSession=2023\%2F2023R&id=sb480;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/} \\
California & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://oag.ca.gov/firearms/ccw} \\
Colorado & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://cbi.colorado.gov/firearms/concealed-handgun-permit-chp-reciprocity} \\
Connecticut & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://portal.ct.gov/despp/division-of-state-police/special-licensing-and-firearms/pistol-permits} \\
Delaware & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://attorneygeneral.delaware.gov/criminal/concealed-carry-deadly-weapons-ccdw/} \\
Florida & 2023 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.flgov.com/eog/news/press/2023/governor-ron-desantis-signs-hb-543-constitutional-carry;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Georgia & 2022 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://gov.georgia.gov/press-releases/2022-04-13/gov-kemp-signs-georgia-constitutional-carry-act-law;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Hawaii & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://www.honolulupd.org/police-services/firearms/} \\
Idaho & 2016 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Illinois & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://isp.illinois.gov/Foid/Ccl} \\
Indiana & 2022 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://events.in.gov/event/gov_holcomb_issues_statement_on_signing_of_hb_1296;  https://www.in.gov/isp/files/Permitless-Carry-Website-Messaging.pdf} \\
Iowa & 2021 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.legis.iowa.gov/legislation/billTracking/billHistory?billName=HF+756&ga=89;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Kansas & 2015 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.kslegislature.gov/li_2016/b2015_16/measures/sb45/;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Kentucky & 2019 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.kentuckystatepolice.ky.gov/ccdw-home/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/} \\
Louisiana & 2024 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://legis.la.gov/Legis/BillInfo.aspx?i=245605;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/} \\
Maine & 2015 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.maine.gov/dps/msp/licenses-permits/concealed-carry-maine;  https://legislature.maine.gov/legis/bills/display_ps.asp?PID=undefined&paper=SP0245&sec0=&snum=127} \\
Maryland & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://mdsp.maryland.gov/Organization/Pages/CriminalInvestigationBureau/LicensingDivision/HandgunPermit.aspx} \\
Massachusetts & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://www.mass.gov/how-to/apply-for-a-firearms-license} \\
Michigan & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://www.michigan.gov/msp/services/ccw} \\
Minnesota & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://dps.mn.gov/divisions/bca/bca-divisions/administrative/Pages/Permit-to-Carry.aspx} \\
Mississippi & 2015 & partial & Yes & Retained in processed panel as 2015 adoption; legal audit marks the row partial. & \detokenize{https://billstatus.ls.state.ms.us/documents/2016/html/HB/0700-0799/HB0786PS.htm;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Missouri & 2017 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.senate.mo.gov/BillTracking/Bills/BillInformation?billPrefix=SB&billSuffix=656&handler=legislation&session=R&year=2016;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Montana & 2021 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://legiscan.com/MT/bill/HB102/2021;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Nebraska & 2023 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://nebraskalegislature.gov/bills/view_bill.php?DocumentID=49710;  https://statepatrol.nebraska.gov/services/concealed-handgun-permits/chp-frequently-asked-questions} \\
Nevada & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://rccd.nv.gov/FeesForms/Brady/CCW-Permit-Recognition/} \\
New Hampshire & 2017 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://legiscan.com/NH/votes/SB12/2017;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
New Jersey & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://www.nj.gov/njsp/firearms/forms.shtml} \\
New Mexico & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://www.dps.nm.gov/concealed-carry/} \\
New York & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://gunsafety.ny.gov/pistol-permit-recertification} \\
North Carolina & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://ncdoj.gov/law-enforcement-training/criminal-justice/officer-certification-programs/concealed-weapon-reciprocity/} \\
North Dakota & 2017 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.nd.gov/ndhp/node/116;  https://legiscan.com/ND/bill/HB1169/2017} \\
Ohio & 2022 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.legislature.ohio.gov//download?key=18965;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Oklahoma & 2019 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.oklegislature.gov/cf_pdf/2019-20\%20SUPPORT\%20DOCUMENTS/BILLSUM/House/HB2597\%20FA4\%20BILLSUM.PDF;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Oregon & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://www.oregon.gov/osp/programs/cjis/pages/oregon-concealed-handgun-license.aspx} \\
Pennsylvania & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/state-laws/concealed-carry-in-pennsylvania/;  https://giffords.org/lawcenter/state-laws/open-carry-in-pennsylvania/;  https://www.pa.gov/en/agencies/psp/programs/firearms/carrying-firearms-in-pennsylvania.html} \\
Rhode Island & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/open-carry/;  https://riag.ri.gov/i-want/get-concealed-carry-permit} \\
South Carolina & 2024 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://sled.sc.gov/constitutional-carry-guidance;  https://legiscan.com/SC/supplement/H3594/id/473107} \\
South Dakota & 2019 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://sdlegislature.gov/Session/Bill/9374;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Tennessee & 2021 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.wvlt.tv/2021/04/08/governor-lee-signs-permitless-carry-into-law/;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Texas & 2021 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://www.lrl.texas.gov/legis/billsearch/billdetails.cfm?billFileID=330877&from=advancedsearch;  https://sll.texas.gov/faqs/permitless-carry-guns/} \\
Utah & 2021 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://bci.utah.gov/concealed-firearm/;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
Vermont & pre-panel & baseline permitless & No & Baseline permitless before the panel; not a within-panel adoption event. & \detokenize{https://www.nraila.org/gun-laws/state-gun-laws/vermont/;  https://www.handgunlaw.us/states/vermont.pdf} \\
Virginia & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://vsp.virginia.gov/services/firearms/resident-concealed-handgun-permits/} \\
Washington & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://dol.wa.gov/professional-licenses/concealed-pistol-license} \\
West Virginia & 2016 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://wvpress.org/breaking-news/wvs-no-permit-concealed-carry-begins-today/;  https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/} \\
Wisconsin & -- & verified non-adopter & No & No statewide permitless concealed-carry adoption through 2024. & \detokenize{https://giffords.org/lawcenter/gun-laws/policy-areas/guns-in-public/concealed-carry/;  https://www.usconcealedcarry.com/blog/what-is-open-carry-and-which-states-allow-it/;  https://www.wisdoj.gov/Pages/PublicSafety/concealed-carry-weapon-license.aspx} \\
Wyoming & 2011 & clean adopter & Yes & Clean source-verified within-panel adopter. & \detokenize{https://legiscan.com/WY/bill/SF0047/2011;  https://www.handgunlaw.us/documents/Permitless_Carry_States.pdf} \\
\bottomrule
\end{longtable}
\endgroup
